\subsection{syncwbern52}
\label{syncwbern52}

\subsubsection{Purpose}
\texttt{syncwbern52.py} is a bash (Shell) script to synchronize (mirror) a local Bernese \texttt{GEN}
directory, with the remote one, which can be found at AIUB's ftp server
\url{fpt://ftp.unibe.ch/aiub/BSWUSER52/GEN/}.\\
\textbf{Location:} \texttt{src/bash/syncwbern52.sh}

\subsubsection{Usage}
\texttt{syncwbern52 [OPTIONS]}\\
at least either \texttt{--target-directory=} or \texttt{--bernese-loadvar=}
must be specified as command line arguments.


Switches:
\begin{itemize}
\item \texttt{-t --target-directory=} /foo/bar\\
Specify the (local) target directory in localhost (See \autoref{sec:syncwbern52_notes}, Note 1).
\item \texttt{-b --bernese-loadvar=} /foo/bar/LOADGPS.setvar\\
Specify a Bernese source file (i.e. the file \texttt{BERN52/GPS/EXE/LOADGPS.setvar}) 
which can be sourced; if such a file is set, then the local target 
directory is defined by the variable \$X/GEN. (See \autoref{sec:syncwbern52_notes}, Note 1)
\item \texttt{-o --logfile=} [logfile]\\
Specify log file. \underline{Default value is /dev/null}.
\item \texttt{-q --quite}\\
Do not show progress on screen.
\item \texttt{-s --stamp-file=} [stampfile]\\
Specify a file where the time stamp of current run will be written, 
so that the user can keep track of when the last mirroring was done.
\item \texttt{-h --help}\\
Display (this) help message and exit.
\item \texttt{-v --version}\\
Dsiplay version and exit.
\end{itemize}

\subsubsection{Prerequisites}
\begin{itemize}
\item \texttt{getopt},
\item \texttt{lftp}, 
\item \texttt{hash}
\end{itemize}

\subsubsection{Exit Status}
On sucess, the program returns \texttt{0}.\\
Else, the return status is $>$0.

\subsubsection{ToDo}
%\begin{tabular}{l l l}
%Date & What & Status\\
%\hline \\
%\end{tabular}

\subsubsection{Bugs}
Send reports to:\\
Xanthos Papanikolaou \href{mailto:xanthos@mail.ntua.gr}{mailto:xanthos@mail.ntua.gr}\\
Demitris Anastasiou  \href{mailto:danast@mail.ntua.gr}{mailto:danast@mail.ntua.gr}\\
Vangelis Zacharis  \href{mailto:vanzach@survey.ntua.gr}{mailto:vanzach@survey.ntua.gr}\\
\bigskip

%\begin{tabular}{l l l}
%Date & What & Status\\
%\hline \\
%\end{tabular}

\subsubsection{Notes}\label{sec:syncwbern52_notes}
\begin{enumerate}[label=\arabic*]
\item Note that if both \texttt{-t} and \texttt{-b} switches are used, 
the target directory is the one specified by the \texttt{-b} option 
(i.e. using the LOADGPS.setvar file).\\
\item All files with \texttt{.EPH} extension will be excluded from synchronization.
\end{enumerate}